Statistical Methods for Replicability Assessment

### 2019-03-15 paper.tex
link to public repo

  A git repository containing with the code generating the images in this article is available at \url{https://kenhung@bitbucket.org/kenhung/reproducibility-in-psychology.git}.

>>>>

  A git repository containing with the code generating the images in this article is available at \url{https://github.com/kenhungkk/assessing-replicability.git}.

\section*{Supplement}

  The supplement is available in the git repository, or directly on \url{https://github.com/kenhungkk/assessing-replicability/raw/public/supplement.pdf}.
